Intelligent Quadcopter for IARC 2018

### 2018-05-31 IARC_Paper_2018/Paper.tex
added canny
More paper working stuff

\usepackage{graphicx,
			amssymb,
			amsmath,
			titlesec,
			lipsum,
			setspace,
			lastpage,
			fancyhdr,
			tikz,
			titling}
\usepackage{tkz-euclide}
\usetkzobj{all}
\usetikzlibrary{shapes,arrows}
\tikzstyle{block} = [rectangle, draw, fill=blue!20,
     text centered, rounded corners, minimum height=2em]
\tikzstyle{line} = [draw, -latex']

@@

%%%%%%%%%%%%%%%%%%%%%% ADD TITLE HERE %%%%%%%%%%%%%%%%%%%%%%
\title{Intelligent Quadcopter for IARC 2018}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%% ABSTRACT %%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Texas Aerial Robotics has constructed a custom quadrotor aircraft for the fulfillment of the International Aerial Robotics Competition Mission 7. A combination of lightweight materials and powerful propulsion enables optimized flight time, while standardized flight control systems supported by a massive community enabled customization and adaptation to the mission at hand. This includes the integration of a multitude of sensors that enhance environmental awareness and allow for the tracking of dynamic entities inherent to the operation using homebrewed algorithms and the significant computing power onboard the aircraft. Safe development has been assured by strategic selection of components, thorough vetting of software in Software in the Loop simulation, and robust testing procedures in secure areas.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section*{INTRODUCTION}
	Previous aerial robotics missions have always allowed for GPS or set navigation points that allowed for constant locational awareness for the drone. Location data is important to any mission, as telemetry prevents various failures, including complete loss of control for the drone. Thus, mission 7 requires novel solution to deriving this critical telemetry, as GPS is forbidden. Additionally, the aircraft must be capable of interacting with ground vehicles without being directly informed of their locations, requiring advanced detection and robust hardware designed for repeated contact.

@@

	\subsection{Yearly Milestones}
	2017 - Have a working bot, with computer vision software in working or nearly working
	2018 - Continue development of computer vision, develop a computational  game strategy through creation of simulations of the motion of roombas, tweak the physique of the drone for better flight control and stability

\section*{Air Vehicle}
	\subsection*{Propulsion and Lift System}
	        The vehicle utilizes a x-y axis symmetrical quad-rotor system. This provides a balanced airframe optimized for omni-directional maneuvering. The frame is lifted by four T-Motor U3 KV700 motors. These motors provide 1.8 [kg] of thrust per motor at 100\% throttle when paired with a 4-cell battery and 13 [in] propellers for total 7.2 [kg] of thrust. This is necessary for our 3.15 kg weight to maintain a 2.2 thrust-to-weight ratio ideal for battery life and flight time. 
			The propellers used with the motors are 13 [in] long and made of carbon fiber. These T-Motor propellers provide excellent precision, durability, and efficiency. The rotors are placed to counter-rotate for flight stability and to retain a one-to-one ratio of propellers to motors.

@@

		\subsubsection*{Navigation}
			We have made slight modifications to the Arducopter firmware, which allow us to set the EKF origin.  This has been done to allow our drone to navigate in GPS denied environments.  For general waypoint navigation, the drone utilizes the Arducopter EKF that takes in data from the  IMU, compass, altitude LIDAR and the optical flow sensor. The EKF position is then queried via mavros, so that our strategy code can use our position to make intelligent decisions. In addition, the strategy node takes in data from computer vision and 2d lidar. The strategy will determine a waypoint and mode, and the ros controls node will do a sanity check on the waypoint, then publish the waypoint until the drone has reached its destination. Over time, the EKF will have error in comparison to reality. To combat this, the control node will input a correction vector.  This correction vector is formed from our computer vision algorithm that recognizes the absolute corners of the grid. This algorithm goes as follows. Gaussian blur, color threshold, erosion, dilation, Hough, line intersection, and non maximum suppression.

@@

		\subsubsection*{Flight Termination System}
			Our drone houses a 40 amp brushless esc connected to a rc receiver, which acts as our kill switch. In the event of catastrophic failure the safety operator can send the kill signal, and all power will be cut to the drone’s systems.

\section*{Payload}
	The Drone has been designed to carry all the necessary GNC sensors, 2d LIDAR, and array of cameras and 3 nvidia TX2 Jetsons. In addition the drone carries a telemetry radio, kill switch and rc receiver in order to carry out safe flight. 
	\subsection*{Sensor Suite}
		\subsubsection*{GNC Sensors}
			The quadcopter uses eight sensors for flight control. The main sensors used for the navigation of the quadcopter are a downwards-facing 1-D LiDAR module, a PX4FLOW optical sensor, and the built-in sensors of our flight control board, the Pixhawk 2.
    		The 1-D LiDAR module used is the LiDAR-lite v3 from Garmin. This one dimensional sensor is directed downwards and provides data that is used to determine altitude. The PX4FLOW sensor measures velocity by comparing frame by frame images and measuring distance travelled and direction. The Pixhawk 2 contains three 3-axis accelerometers, three 3-axis gyroscopes, and two 3-axis compasses. The data from these sensors is used by the Pixhawk onboard system for flight control and the maneuvering of the quadcopter.

		\subsubsection*{Mission Sensors}
			For the goal of completing Mission 7 the drone must be able to detect roombas and obstacles. The quadcopter is equipped with a single downward facing camera, four outward facing cameras, and a two-dimensional plane LiDAR sensor for obstacle avoidance.
			The singular bottom camera is a Logitech C210 webcam. This webcam is used for roomba detection and tracking the targeted roomba for autonomous interaction.For the four peripheral cameras are Logitech 960 C270. These are used to recognize and track the roombas around the playing field. These five webcams provides enough information allowing the drone to incorporate the recognized roombas into the strategy of the autonomous system. 
			The 2D LiDAR sensor is the SWEEP sensor by Scanse.This is a single lidar that rotates to provide a full x-y plane view inline with the z position of the drone for obstacle detection. We chose to use this for obstacle detection rather than four separate LiDARs or webcams to save on computing power.

@@

			% \begin{figure}[!htbp]
			% 	\begin{center}
			% 		\includegraphics[width=0.75\textwidth]{RoombaDetectionImage}
			% 	\end{center}
			% \end{figure}

@@

			In order to transform this pixel coordinate into x-y coordinates relative to the drone, a few key assumptions made are that:

@@

				\begin{align*}
				PIX = \frac{PIX\_MAX}{2}
				\end{align*}

@@

				\begin{align*}
				\phi = z * abs(\frac{PIX}{PIX\_MAX} * \phi - \frac{\phi}{2})
				\end{align*}

@@

						\tab If $PIX$ lies above the center pixel, that is $PIX > \frac{PIX\_MAX}{2}$, Then:

						\begin{align*}
						REAL = z * tan(\theta + \frac{\phi}{2})
						\end{align*}

						\tab If $PIX$ lies below the center pixel, that is $PIX < \frac{PIX\_MAX}{2}$, Then:

						\begin{align*}
						REAL = z * tan(\theta - \frac{\phi}{2})
						\end{align*}

				There are two cases to finding the real coordinate ($REAL$) relative to the drone in the $Y$ direction:

						\tab If $PIX$ lies above the center pixel, that is $PIX > \frac{PIX\_MAX}{2}$

						\begin{align*}
						REAL = z * tan(\theta - \frac{\phi}{2})
						\end{align*}

						\tab If $PIX$ lies below the center pixel, that is $PIX < \frac{PIX\_MAX}{2}$

						\begin{align*}
						REAL = z * tan(\theta + \frac{\phi}{2})
						\end{align*}

				This is different from the x only because top of frame is $1$ and bottom is $MAX\_PIX$, while in $X$ 'top' of frame is $MAX\_PIX$ and bottom is $1$.

		Once the coordinate X,Y in meters is found relative to the drone, it must be transformed into a coordinate that is in the ‘gym reference frame’. The gym reference frame is defined as a right handed coordinate system starting in the bottom left hand corner of the field where the green line meets the outer white line. This transformation is defined as followed.

		\begin{align*}
		yawAngle = currentHeading - GymOffset
		\end{align*}
		\begin{align*}
		roombaPosGym = CR + EKFdronePose + R(3)(YawAngle)*roombaPosDrone 
		\end{align*}
		\[
		R(3) = 
			\begin{bmatrix}
			cos(yawAngle) & -sin(yawAngle) & 0 \\
			sin(yawAngle) & cos(yawAngle)  & 0 \\
			0 & 0 & 1 
			\end{bmatrix}
		\]

		CR is the correction vector formulated from the corner detection vision algorithm. EKFdronePose is the position of the drone queried from the pixhawk. R(3) is the rotation matrix about the third axis. GymOffset is the direction of the 2 axis defined during the startup sequence before flight. The new coordinate in the gym frame is passed off to the strategy node as data to be acted on. 
	\subsection*{Threat Avoidance}
		Our avoidance system takes data from a 2d LiDAR that is used to identify the obstacle roombas. This data is passed and the Strategy node uses this data to weight possible movements negatively based on their relative position to the target roombas. The Control node also will use the data, and in the event an obstacle robot is within 1.5 [m] will issue a waypoint opposite of the minimum vector.

@@

	\subsection*{Power Management System}
		The quadcopter uses  a 10000mAh 4S 10C LiPo battery and a 2000mAh 3S 15C LiPo battery for power. The 10000mAh 4S 10C LiPo is used to power our ESCs and Motors. With 4 T-Motor U3 K700 motors running at close to the ideal 50\% throttle, a 4 Cell battery was necessary to reach the 1800 grams of thrust per motor needed for hovering flight. The 2000mAh 3S 15C LiPo will power the flight control board and Jetson compute units.
		\begin{align*}
		T(min)=Battery power(AH)*60/Total current drawn by motors
		\end{align*}
		Assuming an average throttle of 65\% for maneuvering, we see a 9 A current draw from each motor, and with a 10 Ah battery, that provides us with 16 minutes of flight time with minimal maneuvering and height change. This gives us plenty of headroom for more intense altitude and positioning changes, which will allow us to move more quickly during the competition, a valuable asset with the given time limitation. 
		\begin{align*}
		Max continuous Amp draw (A) = Battery capacity (Ah) * Discharge rate (C)
		\end{align*}
		To save on weight and space, we chose a 10C discharge rate battery, as this is still more than enough to match the maximum continuous current draw of 25 A and maximum practical current draw of 19.4 A required by the motors. The 10000 mAh battery with a 10C discharge rate gives us a maximum continuous current draw of 100 A, matching the limit of the motors.

@@

\section*{Operations}
	\subsection*{Flight Preparations}
		\subsubsection*{Checklist}
			\begin{enumerate}
				\item Check battery voltage (12.0-12.6v) and insert
				\item Make sure LIDAR and PX4FLOW are not covered
				\item Make sure that ESCs are plugged in to the right pins
				\item Make sure prop guards are secure
				\item Make sure that the props are on in the correct direction (leading edge in)
				\item Make sure that the props are not upside down
				\item Make sure props are clear of any structures
				\item Make sure Kill Switch is in off position
				\item Power on controllers
				\item Make sure TELEM2 is unplugged
				\item Plug in power loop
				\item Turn Kill Switch to on position
				\item Make sure ground station has good telemetry
				\item Verify critical sensors are giving good data
				\item Plug in TELEM2
				\item SSH start/verify autonomous scripts are running
				\item Make sure everyone is clear of drone
				\item Verify mode switch in Stabilize
				\item Hold safety button
				\item Mode switch to Autonomous
			\end{enumerate}
	\subsection*{Man/Machine Interface}
		The drone has a DX7 RC controller interface for system checks and emergency situations. In addition, the flight controller can be monitored via a telemetry radio using Mission Planner. Our autonomous scripts must be initiated by an SSH connection to our Nvidia Jetsons.

\section*{Risk Reduction}
	\subsection*{Vehicle Status}
		\subsubsection*{Shock/Vibration Isolation}
		The modern pixhawk flight controller contains internal damping from the vibration of the drone’s structure. The decided there is no need for extra damping. After completion of our first drone last year, flight logs from the Pixhawk confirmed that vibration on the built quadcopter was well within recommended amounts. The team believes there is no need to have landing shocks, because the sophisticated Arducopter flight stack has logic to recognise landing. Because of this, nominal landings will not interfere with the guidance or navigation of the drone.

@@

\section*{Conclusion}
		Texas Aerial Robotics’ solution to the challenges provided by IARC mission 7 are bountiful and diverse. The physical design process, from the ground up, optimizes flight time while enabling the physical contact required for success, Unique software utilizes input from an expansive battery of sensors to overcome the telemetry limitations imparted by the contest and track the dynamic objectives as they move about the area. Safe operation of these vast networks of interlocking components has been ensured through particular hardware selection and thorough vetting.
	\nocite{redmon2016yolo9000}
	\bibliography{bibliography}
	\bibliographystyle{plain}

>>>>

\usepackage{graphicx,
			amssymb,
			amsmath,
			titlesec,
			lipsum,
			setspace,
			lastpage,
			fancyhdr,
			tikz,
			titling}
\usepackage{tkz-euclide}
\usepackage{setspace}

\usetkzobj{all}
\usetikzlibrary{shapes,arrows}
\tikzstyle{block} = [rectangle, draw, fill=blue!20,
text centered, rounded corners, minimum height=2em]

\tikzstyle{line} = [draw, -latex']
\newenvironment{my_enumerate}{
	\begin{enumerate}
	\setlength{\itemsep}{1pt}
	\setlength{\parskip}{0pt}
	\setlength{\parsep}{0pt}}{\end{enumerate}
}

@@

\title{Intelligent Quadcopter for IARC 2018}

@@

%%%%%%%%%%%%%%%%%%%%%%% ABSTRACT %%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
	Texas Aerial Robotics has constructed a custom quadrotor aircraft for the fulfillment of the International Aerial Robotics Competition Mission 7. A combination of lightweight materials and powerful propulsion enables optimizes flight time, while standardized flight control systems supported by a massive community enabled customization and adaptation to the mission at hand. This includes the integration of a multitude of sensors that enhance environmental awareness and allow for the tracking of dynamic entities inherent to the operation using homebrewed algorithms and the significant computing power onboard the aircraft. Safe development has been assured by strategic selection of components, thorough vetting of software in Software in the Loop simulation, and robust testing procedures in secure areas.
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section*{Introduction}
	Previous aerial robotics missions have always allowed for GPS or set navigation points that allowed for constant locational awareness for the drone. Location data is important to any mission, as telemetry prevents various failures, including complete loss of control for the drone. Thus, Mission 7 requires novel solution to deriving this critical telemetry, as GPS is forbidden. Additionally, the aircraft must be capable of interacting with ground vehicles without being directly informed of their locations, requiring advanced detection and robust hardware designed for repeated contact.

@@

	\subsection{Yearly Milestones}
	2017 - Have a working bot, with computer vision software in working or nearly working
	2018 - Continue development of computer vision, develop a computational game strategy through creation of simulations of the motion of Roombas, tweak the physique of the drone for better flight control and stability

\section*{Air Vehicle}
	\subsection*{Propulsion and Lift System}
			The vehicle utilizes a x-y axis symmetrical quad-rotor system. This provides a balanced airframe optimized for omni-directional maneuvering. The frame is lifted by four T-Motor U3 KV700 motors. These motors provide 1.8 [kg] of thrust per motor at 100\% throttle when paired with a 4-cell battery and 13 [in] propellers for total 7.2 [kg] of thrust. This is necessary for our 3.15 kg weight to maintain a 2.2 thrust-to-weight ratio ideal for battery life and flight time.

			The propellers used with the motors are 13 [in] long and made of carbon fiber. These T-Motor propellers provide excellent precision, durability, and efficiency. The rotors are placed to counter-rotate for flight stability and to retain a one-to-one ratio of propellers to motors.

@@

		\subsubsection*{Navigation}
			We have made slight modifications to the Arducopter firmware, which allow us to set the EKF origin. This has been done to allow our drone to navigate in GPS denied environments. For general waypoint navigation, the drone utilizes the Arducopter EKF that takes in data from the IMU, compass, altitude LIDAR and the optical flow sensor. The EKF position is then queried via mavros, so that our strategy code can use our position to make intelligent decisions. In addition, the strategy node takes in data from computer vision and 2d lidar. The strategy will determine a waypoint and mode, and the ros controls node will do a sanity check on the waypoint, then publish the waypoint until the drone has reached its destination. Over time, the EKF will have error in comparison to reality. To combat this, the control node will input a correction vector. This correction vector is formed from our computer vision algorithm that recognizes the absolute corners of the grid. This algorithm goes as follows. Gaussian blur, color threshold, erosion, dilation, Canny, Hough, line intersection, and non maximum suppression.

@@

		\subsubsection*{Flight Termination System}
			Our drone houses a 40 amp brushless esc connected to a rc receiver, which acts as our kill switch. In the event of catastrophic failure the safety operator can send the kill signal, and all power will be cut to the drone's systems.

\section*{Payload}
	The Drone has been designed to carry all the necessary GNC sensors, 2d LIDAR, and array of cameras and 3 nvidia TX2 Jetsons. In addition the drone carries a telemetry radio, kill switch and rc receiver in order to carry out safe flight.
	\subsection*{Sensor Suite}
		\subsubsection*{GNC Sensors}
			The quadcopter uses eight sensors for flight control. The main sensors used for the navigation of the quadcopter are a downwards-facing 1-D LiDAR module, a PX4FLOW optical sensor, and the built-in sensors of our flight control board, the Pixhawk 2.

			The 1-D LiDAR module used is the LiDAR-lite v3 from Garmin. This one dimensional sensor is directed downwards and provides data that is used to determine altitude. The PX4FLOW sensor measures velocity by comparing frame by frame images and measuring distance travelled and direction. The Pixhawk 2 contains three 3-axis accelerometers, three 3-axis gyroscopes, and two 3-axis compasses. The data from these sensors is used by the Pixhawk onboard system for flight control and the maneuvering of the quadcopter.

		\subsubsection*{Mission Sensors}
			For the goal of completing Mission 7 the drone must be able to detect Roombas and obstacles. The quadcopter is equipped with a single downward facing camera, four outward facing cameras, and a two-dimensional plane LiDAR sensor for obstacle avoidance.
			The singular bottom camera is a Logitech C210 webcam. This webcam is used for Roomba detection and tracking the targeted Roomba for autonomous interaction.For the four peripheral cameras are Logitech 960 C270. These are used to recognize and track the Roombas around the playing field. These five webcams provides enough information allowing the drone to incorporate the recognized Roombas into the strategy of the autonomous system.
			The 2D LiDAR sensor is the SWEEP sensor by Scanse.This is a single lidar that rotates to provide a full x-y plane view inline with the z position of the drone for obstacle detection. We chose to use this for obstacle detection rather than four separate LiDARs or webcams to save on computing power.

@@

			\begin{figure}[!htbp]
				\begin{center}
					\includegraphics[width=0.75\textwidth]{roomba}
				\end{center}
			\end{figure}

@@

			\begin{spacing}{.2}
			In order to transform this pixel coordinate into x-y coordinates relative to the drone, a few key assumptions made are that:

@@

				\begin{center}
					$PIX = \frac{PIX\_MAX}{2}$
				\end{center}

@@

				\begin{center}
					$\phi = z * abs(\frac{PIX}{PIX\_MAX} * \phi - \frac{\phi}{2})$
				\end{center}

@@

						\tab If $PIX$ lies above the center pixel, that is $PIX > \frac{PIX\_MAX}{2}$, Then:
						\begin{center}
							$REAL = z * tan(\theta + \frac{\phi}{2})$
						\end{center}
						\tab If $PIX$ lies below the center pixel, that is $PIX < \frac{PIX\_MAX}{2}$, Then:
						\begin{center}
							$REAL = z * tan(\theta - \frac{\phi}{2})$
						\end{center}
				There are two cases to finding the real coordinate ($REAL$) relative to the drone in the $Y$ direction:
						\tab If $PIX$ lies above the center pixel, that is $PIX > \frac{PIX\_MAX}{2}$
						\begin{center}
							$REAL = z * tan(\theta - \frac{\phi}{2})$
						\end{center}
						\tab If $PIX$ lies below the center pixel, that is $PIX < \frac{PIX\_MAX}{2}$
						\begin{center}
							$REAL = z * tan(\theta + \frac{\phi}{2})$
						\end{center}
				This is different from the x only because top of frame is $1$ and bottom is $MAX\_PIX$, while in $X$ 'top' of frame is $MAX\_PIX$ and bottom is $1$.
			\end{spacing}

		Once the coordinate X,Y in meters is found relative to the drone, it must be transformed into a coordinate that is in the 'gym reference frame'. The gym reference frame is defined as a right handed coordinate system starting in the bottom left hand corner of the field where the green line meets the outer white line. This transformation is defined as followed.

		\begin{center}
			$yawAngle = currentHeading - GymOffset$
		\end{center}
		\begin{center}
			$roombaPosGym = CR + EKFdronePose + R(3)(YawAngle)*roombaPosDrone$
		\end{center}

		\[
		R(3) =
			\begin{bmatrix}
			cos(yawAngle) & -sin(yawAngle) & 0 \\
			sin(yawAngle) & cos(yawAngle)  & 0 \\
			0 & 0 & 1
			\end{bmatrix}
		\]

		CR is the correction vector formulated from the corner detection vision algorithm. EKFdronePose is the position of the drone queried from the Pixhawk. R(3) is the rotation matrix about the third axis. GymOffset is the direction of the 2 axis defined during the startup sequence before flight. The new coordinate in the gym frame is passed off to the strategy node as data to be acted on.
	\subsection*{Threat Avoidance}
		Our avoidance system takes data from a 2d LiDAR that is used to identify the obstacle Roombas. This data is passed and the Strategy node uses this data to weight possible movements negatively based on their relative position to the target Roombas. The Control node also will use the data, and in the event an obstacle robot is within 1.5 [m] will issue a waypoint opposite of the minimum vector.

@@

	\subsection*{Power Management System}
		The quadcopter uses a 10000mAh 4S 10C LiPo battery and a 2000mAh 3S 15C LiPo battery for power. The 10000mAh 4S 10C LiPo is used to power our ESCs and Motors. With 4 T-Motor U3 K700 motors running at close to the ideal 50\% throttle, a 4 Cell battery was necessary to reach the 1800 grams of thrust per motor needed for hovering flight. The 2000mAh 3S 15C LiPo will power the flight control board and Jetson compute units.
		\begin{center}
			$T(min) = \frac{\text{Battery power}(AH) * 60}{\text{Total current drawn by motors}}$
		\end{center}

		Assuming an average throttle of 65\% for maneuvering, we see a 9 A current draw from each motor, and with a 10 Ah battery, that provides us with 16 minutes of flight time with minimal maneuvering and height change. This gives us plenty of headroom for more intense altitude and positioning changes, which will allow us to move more quickly during the competition, a valuable asset with the given time limitation.
		\begin{center}
			Max continuous Amp draw ($A$) = Battery capacity ($Ah$) $*$ Discharge rate ($C$)
		\end{center}

		To save on weight and space, we chose a 10C discharge rate battery, as this is still more than enough to match the maximum continuous current draw of 25 A and maximum practical current draw of 19.4 A required by the motors. The 10000 mAh battery with a 10C discharge rate gives us a maximum continuous current draw of 100 A, matching the limit of the motors.

@@

\section*{Operations}
	\subsection*{Flight Preparations}
		\subsubsection*{Checklist}
			\begin{my_enumerate}
				\item Check battery voltage (12.0-12.6v) and insert
				\item Make sure LIDAR and PX4FLOW are not covered
				\item Make sure that ESCs are plugged in to the right pins
				\item Make sure prop guards are secure
				\item Make sure that the props are on in the correct direction (leading edge in)
				\item Make sure that the props are not upside down
				\item Make sure props are clear of any structures
				\item Make sure Kill Switch is in off position
				\item Power on controllers
				\item Make sure TELEM2 is unplugged
				\item Plug in power loop
				\item Turn Kill Switch to on position
				\item Make sure ground station has good telemetry
				\item Verify critical sensors are giving good data
				\item Plug in TELEM2
				\item SSH start/verify autonomous scripts are running
				\item Make sure everyone is clear of drone
				\item Verify mode switch in Stabilize
				\item Hold safety button
				\item Mode switch to Autonomous
			\end{my_enumerate}
	\subsection*{Man/Machine Interface}
		The drone has a DX7 RC controller interface for system checks and emergency situations. In addition, the flight controller can be monitored via a telemetry radio using Mission Planner. Our autonomous scripts must be initiated by an SSH connection to our Nvidia Jetsons.

\section*{Risk Reduction}
	\subsection*{Vehicle Status}
		\subsubsection*{Shock/Vibration Isolation}
		The modern Pixhawk flight controller contains internal damping from the vibration of the drone's structure. The decided there is no need for extra damping. After completion of our first drone last year, flight logs from the Pixhawk confirmed that vibration on the built quadcopter was well within recommended amounts. The team believes there is no need to have landing shocks, because the sophisticated Arducopter flight stack has logic to recognize landing. Because of this, nominal landings will not interfere with the guidance or navigation of the drone.

@@

\section*{Conclusion}
		Texas Aerial Robotics' solution to the challenges provided by IARC Mission 7 are bountiful and diverse. The physical design process, from the ground up, optimizes flight time while enabling the physical contact required for success, Unique software utilizes input from an expansive battery of sensors to overcome the telemetry limitations imparted by the contest and track the dynamic objectives as they move about the area. Safe operation of these vast networks of interlocking components has been ensured through particular hardware selection and thorough vetting.
	\nocite{redmon2016yolo9000}
	\nocite{GitHubSPACEROBOTICS}
	\nocite{HoughTransform}
	\nocite{CannyEdgeDetection}
	\bibliography{bibliography}
	\bibliographystyle{plain}
